Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-11-18 paper/ifo-futureWork.tex
minor changes, commented out footmisc
removing HMM acroymn

\begin{figure*}
	\includegraphics[height=.99\textwidth, angle=-90]{figures/pipeline.pdf}
	\caption{
Flowchart for the signal through the optical microphone. The transfer function would have to account for each stage. 
The stage inside the red-dash box is analysed in Appendix~\ref{app:intensity_derivation}. Understanding the other stages is one aim of future work. 
}
	\label{fig:pipeline_highlighted}
\end{figure*}

@@

A voluminous literature exists on using HMMs trained on phonemes to recognize speech~\cite{HMM_english}. These could perform the final stage of speech enhancement for the optical microphone. Interestingly, this connects back to the Viterbi algorithm in Section~\ref{sec:viterbi_wandering}, which is also underpinned by a HMM, albeit of a different type. Alternatively, machine learning solutions exist throughout the field that are able to compete with statistical techniques such as the logMMSE estimator~\cite{SEGAN}.

>>>>

\begin{figure*}
	\includegraphics[height=.8\textwidth, angle=-90]{figures/pipeline.pdf}
	\caption{
Flowchart for the signal through the optical microphone. The transfer function would have to account for each stage. 
The stage inside the red-dash box is analysed in Appendix~\ref{app:intensity_derivation}. Understanding the other stages is one aim of future work. 
}
	\label{fig:pipeline_highlighted}
\end{figure*}

@@

A voluminous literature exists on using hidden Markov models trained on phonemes to recognize speech~\cite{HMM_english}. These could perform the final stage of speech enhancement for the optical microphone. Interestingly, this connects back to the Viterbi algorithm in Section~\ref{sec:viterbi_wandering}, which is also underpinned by a hidden Markov model, albeit of a different type. Alternatively, machine learning solutions exist throughout the field that are able to compete with statistical techniques such as the logMMSE estimator~\cite{SEGAN}.

### 2020-11-18 paper/ifo-wanderingTone.tex
removing HMM acroymn

Following the method of Refs.~\cite{SuvorovaEtAl:2016,SuvorovaEtAl:2017}, we use a hidden Markov model (HMM) to recover the wandering signal from noisy data. 
In a HMM, the frequency state of the signal is unknown, or hidden, and can undergo transitions at discrete times. 
%To do this, we define the frequency of the signal as a hidden (unknown) state which can undergo transitions at discrete times. 
The transitions are Markovian in that the hidden state (i.e.\ frequency) of the system at any time depends solely on its state at the previous time. The detection statistic (observable) relates the hidden states of the system to the observed data.
The Viterbi algorithm~\cite{Viterbi:1967} is used to find the most probable sequence of states given the sequence of observables.
%To perform the task of recovering the signal, we use the Viterbi algorithm~\cite{Viterbi:1967} to efficiently find the most probable path through the spectrogram given the sequence of observations.
This method is used in continuous wave searches for a variety of astrophysical targets~\cite{ScoX1O2Viterbi:2019, ScoX1ViterbiO1:2017, MillhouseStrangMelatos:2020, JonesSun:2020, MiddletonEtAlO2LMXBs:2020, PostMergerRemnantSearch:2019, SunEtAlSNR:2018, viterbi_application} and forms the basis of the analysis in this section.

>>>>

Following the method of Refs.~\cite{SuvorovaEtAl:2016,SuvorovaEtAl:2017}, we use a hidden Markov model to recover the wandering signal from noisy data. 
In a hidden Markov model, the frequency state of the signal is unknown, or hidden, and can undergo transitions at discrete times. 
%To do this, we define the frequency of the signal as a hidden (unknown) state which can undergo transitions at discrete times. 
The transitions are Markovian in that the hidden state (i.e.\ frequency) of the system at any time depends solely on its state at the previous time. The detection statistic (observable) relates the hidden states of the system to the observed data.
The Viterbi algorithm~\cite{Viterbi:1967} is used to find the most probable sequence of states given the sequence of observables.
%To perform the task of recovering the signal, we use the Viterbi algorithm~\cite{Viterbi:1967} to efficiently find the most probable path through the spectrogram given the sequence of observations.
This method is used in continuous wave searches for a variety of astrophysical targets~\cite{ScoX1O2Viterbi:2019, ScoX1ViterbiO1:2017, MillhouseStrangMelatos:2020, JonesSun:2020, MiddletonEtAlO2LMXBs:2020, PostMergerRemnantSearch:2019, SunEtAlSNR:2018, viterbi_application} and forms the basis of the analysis in this section.
